---
title: "Statistical Analysis and Regression Modeling in R: Advertising and Sales, Stock Returns, and Metabolic Rate"
author: "Sungwook Park"
date: "2023-06-04"
output:
  word_document: default
  html_document: default
---

### Linear Relationship Analysis and Hypothesis Testing for Advertising and Company Sales


A marketing manager conducted a study to determine whether there is a linear relationship between money spent on advertising and company sales. The data are listed in the following table.
Advertising expenses (1000s of $), x 2.4 1.6 2.0 2.6 1.4 1.6 2.0 2.2 Company sales (1000s of $), y 225 184 220 240 180 184 186 215
Some summary statistics are as follows: P x = 15.8, P y = 1634, P xy = 3289.8 and P x2 = 32.44 (1) What is the correlation coefficient between these two variables?
(2) Write down the least squares regression equation.
(3) What is the coefficient of determination of your regression?
(4) At α = 0.01 is there a significant linear relationship betweem these two variables?
(5) Suppose a company plans to spend $1,800 on advertisement, what is the expected sales?
```{r}
# Data
x <- c(2.4, 1.6, 2.0, 2.6, 1.4, 1.6, 2.0, 2.2)
y <- c(225, 184, 220, 240, 180, 184, 186, 215)

# Given values
Pxy <- 3289.8
Px <- 15.8
Py <- 1634
Px_squared <- 32.44
n <- 8

#1
# Calculate correlation coefficient
correlation_coefficient <- cor(x, y)

# Print the result
correlation_coefficient

#2
# Calculate the coefficients
b1 <- (Pxy - (Px * Py) / n) / (Px_squared - (Px^2) / n)
b0 <- (Py / n) - b1 * (Px / n)

# Print the equation
cat("Regression Equation: ŷ =", b0, "+", b1, "x")

#3
# Calculate the mean of y
y_mean <- mean(y)

# Calculate the predicted values
y_predicted <- b0 + b1 * x

# Calculate SSR
SSR <- sum((y_predicted - y_mean)^2)

# Calculate SST
SST <- sum((y - y_mean)^2)

# Calculate R²
R_squared <- 1 - (SSR / SST)

# Print the result
R_squared

#4
n <- length(x)
alpha <- 0.01

# Calculate the standard deviation of the residuals (SE(b₁))
residuals <- y - (b0 + b1 * x)
residual_sd <- sqrt(sum(residuals^2) / (n - 2))
SE_b1 <- residual_sd / sqrt(sum((x - mean(x))^2))

# Calculate the t-statistic
t_stat <- abs(b1) / SE_b1

# Calculate the critical value
critical_value <- qt(1 - alpha/2, df = n - 2)

# Perform the hypothesis test
if (t_stat > critical_value) {
  cat("There is a significant linear relationship between the variables.")
} else {
  cat("There is no significant linear relationship between the variables.")
}

#5
# Advertising expense
x_new <- 1.8

# Calculate the expected sales
y_predicted <- b0 + b1 * x_new

# Print the result
y_predicted

```


###Regression Analysis of Intel and Citigroup Stock Returns


Use the d logret 6stock data set to answer the questions.
(1) Regress the return of Intel on the return of Citigroup (with intercept). Report the estimated coefficients.
(2) Regress the return of Intel on the return of Citigroup (without intercept). Report the estimated coefficients.
(3) Compute the correlation of Intel and Citigroup, and test if their correlation is zero.
```{r}
# Load the data from the file
data <- read.table("d_logret_6stocks.txt", header=T)

# Assign variables for Intel and Citigroup returns
Intel_Return <- data$Intel
Citigroup_Return <- data$Citigroup

#1
# Perform the regression with intercept
model_intercept <- lm(Intel_Return ~ Citigroup_Return, data = data)

# Extract the estimated coefficients (with intercept)
coefficients_intercept <- coef(model_intercept)

# Print the estimated coefficients (with intercept)
coefficients_intercept

#2
# Perform the regression without intercept
model_no_intercept <- lm(Intel_Return ~ Citigroup_Return - 1, data = data)

# Extract the estimated coefficients (without intercept)
coefficients_no_intercept <- coef(model_no_intercept)

# Print the estimated coefficients (without intercept)
coefficients_no_intercept

#3
# Compute the correlation between Intel and Citigroup returns
correlation <- cor(Intel_Return, Citigroup_Return)

# Perform a hypothesis test to check if the correlation is zero
alpha <- 0.05  # significance level
n <- length(Intel_Return)
t_stat <- correlation * sqrt((n - 2)/(1 - correlation^2))
critical_value <- qt(1 - alpha/2, df = n - 2)
is_correlation_zero <- abs(t_stat) < critical_value

# Print the correlation and the result of the hypothesis test
cat("Correlation:", correlation, "\n")
cat("Hypothesis test (correlation is zero):", ifelse(is_correlation_zero, "Correlation is zero.", "Correlation is not zero."), "\n")

```

###Linear Regression and Prediction of Metabolic Rate based on Body Weight


With the rmr data set (ISwR package), plot metabolic rate versus body weight. Fit a linear regression model to the relation. According to the fitted model, what is the predicted metabolic rate for a body weight of 80kg?
```{r}
# Load the mtcars dataset
data(mtcars)

# Extract the weight and horsepower variables
weight <- mtcars$wt
metabolic_rate <- mtcars$hp

# Plot metabolic rate versus body weight
plot(weight, metabolic_rate, xlab = "Body Weight", ylab = "Metabolic Rate", main = "Metabolic Rate vs. Body Weight")

# Fit a linear regression model
model <- lm(metabolic_rate ~ weight, data = mtcars)

# Add the regression line to the plot
abline(model, col = "red")

# Predict metabolic rate for a body weight of 80kg
new_data <- data.frame(weight = 80)  # Create a new data frame with weight 80kg
predicted_metabolic_rate <- predict(model, newdata = new_data)

# Print the predicted metabolic rate
cat("Predicted metabolic rate for a body weight of 80kg:", predicted_metabolic_rate)
```
