---
title: "Statistical Analyses and Regression Models"
author: "Sungwook Park"
date: "2023-06-07"
output:
  word_document: default
  html_document: default
---
Exploratory Data Analysis and Statistical Tests for Stock Returns
#Linear Regression Analysis for Pfizer and AmerExp
```{r}
data <- read.table("d_logret_6stocks.txt", header = TRUE)
model <- lm(Pfizer ~ AmerExp, data = data)
coefficients <- coef(model)
print(coefficients)

```
#Analysis of Variance (ANOVA) for the Linear Model
```{r}
anova_table <- anova(model)
print(anova_table)
```
#Correlation Analysis between Pfizer and AmerExp Returns
```{r}
correlation <- cor(data$Pfizer, data$AmerExp)

cor_test <- cor.test(data$Pfizer, data$AmerExp)

print(correlation)
print(cor_test)
```
#Proportion Test for Returns Comparison
```{r}

returns_AmerExp <- data$AmerExp
returns_Intel <- data$Intel

prop_test <- prop.test(sum(returns_AmerExp > returns_Intel), length(returns_AmerExp))

print(prop_test)
```
#Analysis of Variance (ANOVA) for Multiple Returns Groups
```{r}
returns_Exxon <- data$Exxon
returns_AmerExp <- data$AmerExp
returns_Pfizer <- data$Pfizer

returns_data <- data.frame(Group = c(rep("Group 1", length(returns_Exxon)), rep("Group 2", length(returns_AmerExp)), rep("Group 3", length(returns_Pfizer))),
                           Returns = c(returns_Exxon, returns_AmerExp, returns_Pfizer))
anova_result <- aov(Returns ~ Group, data = returns_data)
print(summary(anova_result))

```




Exploring Regression Models and Variable Selection for Cement Data
#Linear Regression Model for Cement Data
```{r}
library(MASS)

data(cement, package = "MASS")

model <- lm(y ~ x1 + x2 + x3 + x4 - 1, data = cement)

coefficients <- coef(model)

print(coefficients)

```
#Calculating Adjusted R-Squared
```{r}
adjusted_r_squared <- summary(model)$adj.r.squared

print(adjusted_r_squared)
```
#Identifying Best Subset Regression Model
```{r}
library(leaps)

best_subset <- regsubsets(y ~ x1 + x2 + x3 + x4, data = cement, nbest = 1, nvmax = 2, method = "exhaustive")

best_model <- summary(best_subset)

print(best_model)

#the best model with 2 independent variable is x1 and x2
```



Analyzing Data Sets with Normality Tests, Homogeneity Test, and One-Way ANOVA
#Assessing Normality of Data Sets
```{r}
tredecula <- c(0.09, 0.17, 0.19, 0.16, 0.27, 0.15, 0.25, 0.16, 0.14)
tredecassini <- c(0.28, 0.15, 0.22, 0.11, 0.20, 0.17, 0.23, 0.18, 0.23)
tredecim <- c(0.28, 0.29, 0.14, 0.18, 0.32, 0.39, 0.33, 0.26, 0.12)

shapiro.test(tredecula)$p.value >= 0.1
shapiro.test(tredecassini)$p.value >= 0.1
shapiro.test(tredecim)$p.value >= 0.1

```
#Testing for Homogeneity of Variances
```{r}
bartlett.test(list(tredecula, tredecassini, tredecim))$p.value >= 0.1
```
#Conducting One-Way ANOVA
```{r}

anova_result <- aov(c(tredecula, tredecassini, tredecim) ~ rep(c("tredecula", "tredecassini", "tredecim"), each = 9))
summary(anova_result, alpha = 0.1)

```


Analyzing Relationship Between Smoking and Age Using Chi-Square Test
#Creating and Displaying Data Set
```{r}
age <- c("20-30", "30-40", "40-50", "50-60")
smoke_yes <- c(4, 10, 14, 5)
smoke_no <- c(6, 18, 20, 10)

data <- data.frame(age, smoke_yes, smoke_no)
colnames(data) <- c("Age", "Smoke Yes", "Smoke No")

print(data)


```
#Conducting Chi-Square Test for Independence
```{r}
result <- chisq.test(data[, 2:3])
p_value <- result$p.value

if (p_value <= 0.1) {
  print("The group (smoke and non-smoke) and the Age range effects are dependent.")
} else {
  print("The group (smoke and non-smoke) and the Age range effects are independent.")
}
```
#Exploring Expected Values
```{r}
expected_values <- result$expected
print(expected_values)

```


